Proposed Solution

### 2016-05-06 CAV/evaluation.tex
Updates from ShareLaTeX

\begin{table}[t]
\centering
\caption{Benchmarks for misconfiguration detection}
\label{table:res}
\begin{tabular}{l|l|l}
Error Type       & Passing Tests & False Positives  \\ \hhline{=|=|=}
Missing Entry    & 5/5           & 1, 0, 0, 0, 1        \\ \hline
Type Error       & 5/5           & 0, 0, 0, 0, 0          \\ \hline
Keyword Ordering & 5/5           & 0, 1, 1, 0, 10       \\ \hline
Value Relations  & 4/5           & 0, 1, 0, 0, 0        \\ 
\end{tabular}
\end{table}
%\vspace{-5em}

>>>>

\begin{table}[t]
\centering
\caption{Benchmarks for misconfiguration detection}
\label{table:res}
\begin{tabular}{l|l|l}
Error Type       & Passing Tests & False Positives  \\ \hhline{=|=|=}
Missing Entry    & 5/5           & 1, 0, 0, 0, 4        \\ \hline
Type Error       & 5/5           & 0, 0, 0, 0, 0          \\ \hline
Keyword Ordering & 5/5           & 0, 2, 1, 0, 6       \\ \hline
Value Relations  & 4/5           & 0, 0, 0, 1, 0        \\ 
\end{tabular}
\end{table}
%\vspace{-5em}
